### 2015-02-26 paper_30_measure.tex
finished chapter 3

        How can the PIs, RIs, KRIs, and KPIs be combined to form a single
        value called an MPI (Master Performance Indicator)?

>>>>

        How can the PIs, RIs, KRIs, and KPIs be combined to form a single
        value called an MPI (Master Performance Indicator)?  If the indicators
        are targeted for upper management to understand performance, then 
        KPIs are not the correct indicators.  KPIs are targeted towards
        immediate action and future performance.  RIs and KRIs are the most
        beneficial for upper management to gauge how an organization is doing.
        However, with so many possible RIs and even KRIs, it can be tricky
        to gain a quick understanding.  The next section will present
        and explain a technique to combine KRIs into a single number
        for immediate and  effortless evaluation of an SDO.
